Leaf traits drive differences in biomass partitioning among major plant functional types

### 2015-08-14 manuscript.Rnw
Moved histogram figure to main text

%% uncomment this after compiling the ms, then compile again. This is a recursive dependency :(
% Also, requires Perl.
% #' <<>>=
% #' shell("texcount manuscript.tex > wordcount.txt")
% #' nrw <- get_wordcount("wordcount.txt")
% #' @
% #' 
% #' Total number of words: \Sexpr{nrw$Total} \\
% #' Abstract: \Sexpr{nrw$Abstract} \\
% #' Introduction: \Sexpr{nrw$Introduction} \\
% #' Methods and Materials: \Sexpr{nrw$Methods} \\
% #' Results: \Sexpr{nrw$Results} \\
% #' Discussion: \Sexpr{nrw$Discussion} \\
% #' 
% #' Number of figures: 4 (all in colour) \\
% #' Number of tables: 1 \\
% #' Supporting information : 5 Tables, 5 Figures and 1 Notes.

@@

>>>>

%% uncomment this after compiling the ms, then compile again. This is a recursive dependency :(
% Also, requires Perl.
% #' <<>>=
% #' shell("texcount manuscript.tex > wordcount.txt")
% #' nrw <- get_wordcount("wordcount.txt")
% #' @
% #' 
% #' Total number of words: \Sexpr{nrw$Total} \\
% #' Abstract: \Sexpr{nrw$Abstract} \\
% #' Introduction: \Sexpr{nrw$Introduction} \\
% #' Methods and Materials: \Sexpr{nrw$Methods} \\
% #' Results: \Sexpr{nrw$Results} \\
% #' Discussion: \Sexpr{nrw$Discussion} \\
% #' 
% #' Number of figures: 6 (all in colour) \\
% #' Number of tables: 2 \\
% #' Supporting information : 1 Tables, 3 Figures and 1 Notes.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{FigureS5.pdf}
    \caption{Plant functional types diverge strongly in mass-based partitioning, but converge in area-based partitioning. Shown are histograms (as probability density functions) of leaf mass per area ($M_F/A_F$), leaf mass per unit basal stem area ($M_F/A_S$) and leaf area per unit basal stem area ($A_F/M_S$) grouped by the three PFTs. Arrows indicate means by PFT.}
    \label{fig:fighist}
\end{figure}

### 2015-08-14 manuscript_suppinfo.Rnw
Moved FigS2 to main manuscript; fixed caption table1
Moved histogram figure to main text

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{FigureS2.pdf}
    \caption{Raw data for leaf biomass ($M_F$) and total above-ground woody biomass ($M_S$) for each of the PFTs, as a function of total plant height ($H$). Each point is an individual plant.}
    \label{fig:figureS2}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{FigureS3.pdf}
    \caption{Leaf area ratio ($A_F/M_T$) by PFT. Each symbol is an individual plant. Lines are generalized additive model fits using species/dataset as a random effect. Shaded areas are approximate 95\% confidence intervals.}
    \label{fig:figureS3}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{FigureS5.pdf}
    \caption{Plant functional types diverge strongly in mass-based partitioning, but converge in area-based partitioning. Shown are histograms (as probability density functions) of leaf mass per area (an index of leaf construction cost) ($M_F/A_F$), leaf mass per unit basal stem area ($M_F/A_S$) and leaf area per unit basal stem area ($A_F/M_S$) grouped by the three major plant functional types. Arrows indicate means by PFT.}
    \label{fig:figures5}
\end{figure}

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{FigureS3.pdf}
    \caption{Leaf area ratio ($A_F/M_T$) by plant height (H) and PFT. Each symbol is an individual plant. Lines are generalized additive model fits using species/dataset as a random effect. Shaded areas are approximate 95\% confidence intervals.}
    \label{fig:figureS3}
\end{figure}

@@
